\documentclass[11pt,a4paper]{article}
\usepackage{fourier,graphicx} 
\usepackage{amsmath,amsbsy,bm,amssymb,enumerate,mathrsfs}
 
% Encoding settings
\usepackage[utf8]{inputenc} 
\usepackage{utf8math}
\usepackage{anysize} 


\newcommand{\smat}[1]{ \big(\begin{smallmatrix} #1 \end{smallmatrix}\big)}


\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\Spa}{span}



\renewcommand{\epsilon}{\varepsilon}

\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\RR}{\mathbb{R}}
\DeclareMathOperator{\ZZ}{\mathbb{Z}}
\DeclareMathOperator{\argmin}{\mathrm{argmin}}
\DeclareMathOperator{\CVP}{\mathrm{CVP}}
\DeclareMathOperator{\E}{\mathcal{E}}
\DeclareMathOperator{\V}{\mathcal{V}}
% \DeclareMathOperator{\conv}{\mathrm{conv}}
%\DeclareMathOperator{\cone}{\mathrm{cone}}
%\pagestyle{fancyplain}



\title{Integer Optimization  \\ Problem Set 10 }

%\author{ Friedrich Eisenbrand}
%  \\
%   EPFL\\
%   Switzerland\\
%   {\small \texttt{friedrich.eisenbrand@epfl.ch}}}}
% } 


\date{ April 29, 2024}



\begin{document}

\maketitle 


\begin{enumerate}

  \item Is the Voronoi cell with respect to the $l_\infty$ norm convex? If so, prove it and if not give a counterexample. 

  \item Prove that $\V⊆B(0,n\cdotλ_n(Λ))$ where $\V$ is the Voronoi cell of the full-dimensional lattice $Λ⊆ ℝ^n$.

  \item Let $P = \{p_1,p_2,p_3\} ⊆ ℝ^n$ be a finite set of three  points. Show that the Voronoi cells $\V(p_1), \V(p_2)$ and $\V(p_3)$ intersect in one point.  Show that this point is equidistant from all points $p_1, p_2, p_3$. Show that it is the center of the circle passing through these ppoints, and this circle contains no other points in its interior.

  \item Given any $n$ points in $\mathbb{R}^2$, show that their Voronoi diagram has at most $2n-5$ vertices and $3n-6$ edges.

  \item Given a set of points $S⊆ ℝ^2$ and $p ∈ S$. Show that the region $\V(p)$ is unbounded if and only if $p$ is an extreme point of $\conv(S)$. 

  \item Given $4n$ points in the plane in general position and a line not passing through any of them that has $2n$ points on each side, prove the existence of another line that partitions the plane into $4$ regions, each one with exactly $n$ points.


    \item Show that the voronoi cell of the dual lattice satisfies $$\V(Λ^\ast) =\conv\left\{ \frac{2}{\Vert z \Vert_2^2} z：z∈Λ\setminus\{ 0 \}\right\}.$$


    \item Let $P = \{ x ∈ ℝ^n : Ax ≤ b \} ⊆ ℝ^n$ be a full-dimensional polytope. An inequality $a^Tx ≤ β$ of $Ax ≤ b$ is \emph{redundant} if the inequalities obtained by  removing $a^Tx ≤ β$ from  $Ax ≤ b$ define the same polytope $P$. Let $A'x ≤b'$ be the result of the removal of  $a^Tx ≤ β$ from $Ax ≤ b$.
      \begin{enumerate}[i)] 
      \item Show that  $a^Tx ≤ β$ is redundant if and only if
        \begin{displaymath}
          \max\{ a^T x ： x ∈ ℝ^n, \, A'x ≤ b'\} ≤ β.
        \end{displaymath}
      \item Show that  $a^Tx ≤ β$ is redundant if and only if there exists $λ ∈ ℝ^{m-1}_{≥0}$ such that
        \begin{displaymath}
          a^T = λ^T A' \text{ and } λ^T b' ≤ β. 
        \end{displaymath}
        \emph{Hint: Linear programming duality.}
        \item Show that  $a^Tx ≤ β$ is redundant if and only if the affine dimension of the face $F = \{ x ∈ P ： a^Tx = β\}$ is at most $n-2$, in other words, if and only if  $F$  is not a facet. 
      \end{enumerate}
      
      

\end{enumerate}


%\bibliographystyle{abbrv}
%\bibliography{books,mybib,papers,my_publications}


 
\end{document}





%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
