\documentclass[11pt,a4paper]{article}
\usepackage{fourier,graphicx} 
\usepackage{amsmath,amsbsy,bm,amssymb,enumerate,mathrsfs}
 
% Encoding settings
\usepackage[utf8]{inputenc} 
\usepackage{utf8math}
\usepackage{anysize} 


\newcommand{\smat}[1]{ \big(\begin{smallmatrix} #1 \end{smallmatrix}\big)}


\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\Spa}{span}
\DeclareMathOperator{\interior}{int}


\renewcommand{\epsilon}{\varepsilon}

\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\RR}{\mathbb{R}}
\DeclareMathOperator{\ZZ}{\mathbb{Z}}
\DeclareMathOperator{\argmin}{\mathrm{argmin}}
\DeclareMathOperator{\CVP}{\mathrm{CVP}}
\DeclareMathOperator{\E}{\mathcal{E}}
\DeclareMathOperator{\V}{\mathcal{V}}
% \DeclareMathOperator{\conv}{\mathrm{conv}}
%\DeclareMathOperator{\cone}{\mathrm{cone}}
%\pagestyle{fancyplain}



\title{Integer Optimization  \\ Problem Set 12 }

%\author{ Friedrich Eisenbrand}
%  \\
%   EPFL\\
%   Switzerland\\
%   {\small \texttt{friedrich.eisenbrand@epfl.ch}}}}
% } 


\date{ May 13, 2024}



\begin{document}

\maketitle 


\begin{enumerate}

\item Let $P$ and $Q$ be two simple polygons in $\mathbb{R}^2$, where $P$ has $m$ vertices and $Q$ has $n$ vertices. What is the maximum number of vertices on the boundary of the Minkowski sum $P ⊕ Q$ (asymptotically) assuming:
\begin{enumerate}
    \item $P$ and $Q$ are both convex
    \item $P$ is convex but $Q$ is arbitrary
    \item $P$ and $Q$ are both arbitrary
\end{enumerate}

\item As the leader of an oil-exploration drilling venture, you must determine the least-cost selection of 5 out of 10 possible sites. Label the sites $S_1 , S_2 ,\hdots, S_{10}$ , and the exploration costs associated with each as $C_1 ,C_2 ,\hdots,C_{10}$.
Regional development restrictions are such that:
\begin{enumerate}
    \item Evaluating sites $S_1$ and $S_7$ prevents you from exploring $S_8$.
    \item Evaluating site $S_3$ or $S_4$ prevents you from assessing site $S_5$
    \item Of the sites $S_5, S_6, S_7, S_8$ only two sites may be assessed. 
\end{enumerate}
Formulate an integer program to determine the minimum-cost exploration scheme that satisfies these restrictions.

\item Three different items are to be routed through three machines. Each item must be processed first on machine 1, then
on machine 2, and finally on machine 3. The sequence of items may differ for each machine. Assume that the times
$t_{ij}$ required to perform the work on item $i$ by machine $j$ are known and are integers. Our objective is to minimize the total time necessary to process all the items.
\begin{enumerate}
    \item Formulate the problem as an integer programming problem.
    \item Suppose we want the items to be processed in the same sequence on each machine. Change the formulation accordingly.
\end{enumerate}

\item Let $A$ be a totally unimodular matrix in $\mathbb{R}^{m \times n}$ with rows $A_1, \hdots, A_m$. Let $\delta$ be the maximal value such that for every choice of $n$ rows $A_{i1}, \hdots, A_{in}$ either 
\begin{enumerate}
    \item $A_{in} \in \text{span}(A_{i1}, \hdots, A_{i(n-1)})$ or 
    \item $\text{dist}(A_{in}, \text{span}(A_{i1}, \hdots, A_{i(n-1)})) \geq \delta$. 
\end{enumerate}
Show that $\delta \geq \frac{1}{n}$. 

\item A set $S$ is in isotropic position if for a random point $x ∈ S$, \begin{enumerate}
    \item $\mathbb{E}[x] = 0 $
    \item $\forall v \in \mathbb{R}^n, \mathbb{E}[(v^Tx)^2] = \Vert v \Vert^2$
\end{enumerate}
Prove the following two claims:
\begin{enumerate}[(i)]
    \item $x \in S$ satisfies the above conditions if and only if $\mathbb{E}[xx^T ] = I$.
    \item Any convex set can be put in isotropic position by an affine transformation.
\end{enumerate}



\end{enumerate}


%\bibliographystyle{abbrv}
%\bibliography{books,mybib,papers,my_publications}


 
\end{document}





%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
