\documentclass[11pt,a4paper]{article}
\usepackage{fourier,graphicx} 
\usepackage{amsmath,amsbsy,bm,amssymb,enumerate,mathrsfs}
 
% Encoding settings
\usepackage[utf8]{inputenc} 
\usepackage{utf8math}
\usepackage{anysize} 


\newcommand{\smat}[1]{ \big(\begin{smallmatrix} #1 \end{smallmatrix}\big)}


\DeclareMathOperator{\vol}{vol}
\DeclareMathOperator{\Spa}{span}

\renewcommand{\epsilon}{\varepsilon}

\renewcommand{\leq}{\leqslant}
\renewcommand{\geq}{\geqslant}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\RR}{\mathbb{R}}
\DeclareMathOperator{\ZZ}{\mathbb{Z}}

%\pagestyle{fancyplain}



\title{Integer Optimization  \\ Problem Set 2 }

%\author{ Friedrich Eisenbrand}
%  \\
%   EPFL\\
%   Switzerland\\
%   {\small \texttt{friedrich.eisenbrand@epfl.ch}}}}
% } 


\date{ February 26, 2024}



\begin{document}

\maketitle 




\begin{enumerate} 
\item

  Let $Λ ⊆ ℝ^n$ be a lattice and $v ∈ Λ \setminus \{0\}$ be a shortest vector, i.e., a nonzero lattice vector of minimum norm $\| ⋅ \|_2$. We have seen in class that $Λ' = \{π(v) ： v ∈ Λ\} ⊆ ℝ^n$ is a lattice and therefore has a basis $b_1',\dots,b_k'$. Recall that $π(u) = u - λ v$ where $λ ∈ ℝ$ satisfies $(u - λ v ) \, ⊥ v$.

Let $b_1,\dots,b_k ∈ Λ$ such that $π(b_i) = b_i'$ for each $i$. Show the following:

  \begin{enumerate}[i)] 
  \item $b_1,\dots,b_k,v$ are linearly independent. \label{item:1}
  \item The vectors $b_1,\dots,b_k,v$ generate $Λ$. \label{item:2}
  \end{enumerate}

Give an example of a lattice $Λ ⊆ ℝ^2$ where \ref{item:2} cannot be concluded if $v$ is not a shortest vector in the lattice. 


\item Let $Λ(A)⊆ \RR^n$ be a lattice, where $A∈\RR^{n×n}$ is non-singular. Define the set
  $$Λ^∗=\left\{y∈ \RR^n:y^Tv∈ \ZZ \text{ for each }v ∈ Λ\right\}.$$
  Show that $Λ^∗$ is a lattice. Determine a basis of $Λ^∗$. What is $det(Λ^∗)$?\\
\textit{$Λ^∗$ is called the dual lattice of $Λ$.}

\item Let $Λ⊆\RR^n$ be a full rank lattice. Assume $b_1,\hdots,b_n ∈ Λ$ are linearly independent and that minimize $|\det(b_1, \hdots ,b_n)|$
over all $n$ linearly independent lattice vectors. Prove that $b_1, \hdots ,b_n$ is a basis of $Λ$.

\item Let $B ∈ \mathbb{Q}^{n×n}$ be a lattice basis that consists of pairwise orthogonal vectors. Prove that the shortest vector
of $Λ(B )$ is the shortest column vector of $B$.

\item Given a lattice $Λ$, we denote by $λ_k(Λ) ∈ \RR_{>0}$ the minimal number so that $B(0,λ_k)$ contains $k$ linearly independent lattice vectors. Show that for any lattice $Λ ⊆ \RR^n , λ_1 (Λ) \cdot λ_n (Λ^∗) \geq 1$.

\item Let $Λ ⊂ \RR^d$ be a full-dimensional lattice and let $u_1,\hdots,u_d$ be a set of vectors from $Λ$ such that the volume of the parallelepiped

$$\{α_1u_1 +\hdots+α_du_d, \quad 0\leq α_i\leq1 \quad \text{ for } i=1,\hdots,d\}$$

 is equal to $\detΛ$. Prove that $u_1,\hdots ,u_d$ is a basis of $Λ$.
 

  

\end{enumerate}



%\bibliographystyle{abbrv}
%\bibliography{books,mybib,papers,my_publications}


 
\end{document}





%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
